---
title: "vector_str"
author: "Shan Jiang"
date: "10/30/2018"
output: github_document
---
## R Data Type

R has five basic or "atomic" classes of objects.

* character
* numeric
* integer
* complex
* logical(True/False)

\newline
The basic object is a **vector**. 
Everything in a vector has to be the **same class**. 
But the only exception is a *list*, which is represented as a vector but can contain objects of different classes(indeed, that's why we use them).
```{r}

```
#### Numbers
* The Numbers are treated as double precision real value.  

```{r}
cha_1 = c("1")
class(cha_1)

num_1 = c(1)
class(num_1)
```

* If you expilicitly wants to have an interger, then add an *L* as a suffix.
```{r}
# int_1 as integer, capitalized L gets you the integer 
int_1 = c(1L)
class(int_1)

# Infinity in the special number, stands for infinity
inf_1 = c(1/Inf)
inf_1 
```
The objects can have alot of attributes and can be shown as:
```{r}
# length, which you can determine with length().
x <- list("a", "b", 1:10)
length(x)

# Scalars may have 
x <- c("a", "b", 1:10)
length(x)
```

```{r}
# Its type, which you can determine with typeof().
typeof(letters)

typeof(1:10)
```



* *NaN* stands for "not a number".


#### C Function

concatenate = c  
```{r}
library(tidyverse)
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "jeff")
## [1] FALSE FALSE FALSE  TRUE

str_replace(string_vec, "jeff", "Jeff")

```

* Explicit Coercion in the R.
```{r}
string_vec = as.logical(string_vec)
```

## list 
list can be of anything and can be consisted of any type of data.
```{r}
model_ls = list("a", "90", "T")
```

## Factor 
```{r}
x <- factor(c("yes", "no", "yes", "no", "yes"))
table(x)
unclass(x)

## tell r to use the yes as the baseline level
x <- factor(c("yes", "no", "yes", "no", "yes"), levels = c("yes", "no"))
x
```

